---
title: "451Project"
author: "Ling Ma"
date: "10/8/2020"
output: html_document
---
# Data Preprocessing
```{r}
# Loading
library(dplyr)
library(naniar)
```

`ODA`: official development assistance
`OOF`: Other Official Flows
`aid_total`:total aid
`polity2`:Recipient Polity Score,  "-10 (hereditary monarchy) to +10 (consolidated democracy)"
`oda_gni`: ODA in percentage in gross national income
`gdp_percap_real`:Recipient GDP Per Capita

`population`: Recipient Population
`recipient_trade_world`:Recipient Total Trade with World
`gdp_per_growth`: GDP per capita growth
`GDP_total_growth`: GDP total growth

```{r pressure, echo=FALSE}
data = read.csv("processed.csv")
data
```
First, let's visualize the distribution of the missing data.
```{r}
vis_miss(data)
vis_miss(data,cluster = TRUE)
```

# U.S. impact on recipents

we decide to drop the observations that have missing values for the following reason:
1. "MNAR: Missing Not at Random - the missing is not random, it correlates with unobservable characteristics unknown to a researcher."
2. we still have 80% data left.

```{r}
usdata = data %>%
  select(-Chinese_ODA,-Chinese_aid_total) %>%
  na.omit(data)
```

